intro

### 2022-02-17 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd

The postulation of *adaptive* and *maladaptive* strategies was put into a new perspective with the concept of ER flexibility.
Similar to other psychological domains such as attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals [@Aldao2015].
In contrast, *adaptive* ER requires having a large repertoire of ER strategies to choose from [@Aldao2015] and choosing the strategy that is useful for goal achieving in a particular situation.
This greater ER variability has been shown to be related to reduced negative affect [@Blanke2020].
The process of choosing an ER strategy from one's own repertoire likely shares similarities with other contexts such as intertemporal choice, in which individuals assign subjective values to every choice option [@Kable2007].
Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g. monetary incentives), motivational determinants (i.e. hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
Effort in particular appeared to be the main factor in ER choice behaviour in our previous work [@Scheffel2021].
In that study, participants used the strategies distancing and suppression while inspecting emotional pictures, and could choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one for them - in this case: Suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
Research on ER choice has shown that individuals choose a strategy that they prefer for different, relatively well-known reasons.
However, nothing has been investigated regarding the strategy that is *not* chosen.

>>>>

The postulation of *adaptive* and *maladaptive* strategies was put into a new perspective with the concept of ER flexibility.
Similar to other psychological domains such as attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals [@Aldao2015].
In contrast, *adaptive* ER requires having a large repertoire of ER strategies to choose from [@Aldao2015] and choosing the strategy that is useful for goal achieving in a particular situation.
This greater ER variability has been shown to be related to reduced negative affect [@Blanke2020].
The process of choosing an ER strategy from one's own repertoire likely shares similarities with other contexts such as intertemporal choice, in which individuals assign subjective values to every choice option [@Kable2007].
Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
Effort in particular appeared to be the main factor in ER choice behaviour <!-- chekcne pob bei NHB AE oder BE genutzt wird -->in our previous work [@Scheffel2021].
In that study, participants used the strategies distancing and suppression while inspecting emotional pictures, and could choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one for them - in this case: Suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
Research on ER choice has shown that individuals choose a strategy that they prefer for different, relatively well-known reasons.
However, nothing has been investigated regarding the strategy that is *not* chosen.
